### 2014-10-18 fundamentals/impl.tex
no

The core of the simulator creates a set of key classes on which agent plugins 
are based. In addtion, a set of key tools are also provided, to enrich the API 
and provide a robust suite of behaviors for the developer.

@@

Agent plugins utilize the generic core API to interact with one another. 
Mainly they do this by trading resources.

>>>>

The core of the simulator creates a set of key classes on which agent plugins 
are based. In addtion, a set of key tools are also provided to enrich the API 
and provide a robust suite of behaviors for the developer.

@@

Agent plugins utilize the generic core API to interact with one another.  For 
example, agents rely on the dynamic loading and paradigm for clean plugin 
behavior at the start of the simulation. They also use the resource exchange 
paradigm \gls{API} for trading resources with one another.
